SVG: The Paper

### 2022-05-05 Analysis/index_prpic.Rmd
Prpic model param plot
working on graph a little

Terminology questions:
- item v target
- participant v observer

@@

# compute the average weight for each participant x condition x item selection
# also compute the proportion of times in which the item selected by the 
# participant was judged the most likely to be selected by our model.
a %>% group_by(condition, observer, found) %>%
  summarise(meanb = mean(b),
            prop_best = mean(selected_max), .groups = "drop") %>%
  # finally, also compute what we would expect under a null-model
  mutate(chance = 1/(41-found))-> a_agg
```

@@

# plot target selected weights
ggplot(a_agg, aes(x = found, y = meanb, colour = condition, fill = condition)) + 
  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0, alpha = 0.2) + 
  stat_lineribbon(.width = 0.67, alpha = 0.50) +
  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
                          aes(y = chance), linetype = 2, colour = "black") + 
  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
  scale_y_continuous("average weight from model", expand = c(0.01, 0.01)) -> plt_b

ggplot(a_agg, aes(x = found, y = prop_best, colour = condition, fill = condition)) + 
  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0.00, alpha = 0.2) + 
  stat_lineribbon(.width = 0.67, alpha = 0.50) +
  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
            aes(y = chance), linetype = 2, colour = "black") + 
  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
  scale_y_continuous("proportion most likely was selected", expand = c(0.01, 0.01)) -> plt_c

@@

```{r, echo = TRUE}
my_breaks <- seq(0.0, 1, 0.05)

a %>% mutate(b_bin = cut(max_b, breaks = my_breaks, labels = FALSE)) %>%
  group_by(condition, b_bin) %>% 
  summarise(acc = mean(selected_max), .groups = "drop") %>%
  mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) -> a_cut
```

>>>>

# Ppric Model

```{r}
m <- readRDS("scratch/squirrel.model")
source("functions/plot_spatial_model.R")
plot_fixed_effects(m) + theme(legend.position = "right")
ggsave("../Figures/prpic_model_params.pdf",  width = 8, height = 6)
```

@@

# compute the average weight for each participant x condition x item selection
# also compute the proportion of times in which the item selected by the 
# participant was judged the most likely to be selected by our model.
a %>% group_by(condition, observer, found) %>%
  summarise(meanb = mean(b),
            prop_best = mean(selected_max), .groups = "drop") -> a_agg
```

@@

# plot target selected weights
ggplot(a_agg, aes(x = found, y = meanb, colour = condition, fill = condition)) + 
  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0, alpha = 0.2) + 
  stat_lineribbon(.width = 0.67, alpha = 0.50) +
  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
  scale_y_continuous("average weight from model", expand = c(0.01, 0.01)) -> plt_b

ggplot(a_agg, aes(x = found, y = prop_best, colour = condition, fill = condition)) + 
  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0.00, alpha = 0.2) + 
  stat_lineribbon(.width = 0.67, alpha = 0.50) +
  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
  scale_y_continuous("proportion most likely was selected", expand = c(0.01, 0.01)) -> plt_c

@@

```{r, echo = TRUE}
my_breaks <- seq(0.5, 1, 0.05)

a %>% mutate(b_bin = cut(max_b, breaks = my_breaks, labels = FALSE)) %>%
  group_by(condition, b_bin) %>% 
  summarise(acc = mean(selected_max), .groups = "drop") %>%
  mutate(b_bin = my_breaks[b_bin]) -> a_cut
```
